## Loading required libraries
```{r}
library(ggplot2)
library(ggmap)
library(shiny)
library(leaflet)
library(leaflet.extras)
library(dplyr)
library(osrm)
library(leaflet.minicharts)
```
## Read the data from file
## Please make sure the files are in the /FD0x/place_visit_data folder that in the same directory with this code 
```{r}
# Read GLH data for FD01
# Read and preprocess the data files
data_FD01 <- read.csv("/FD01/place_visit_data/FD01_place_visit.csv")
data_FD01 <- data_FD01 %>%
  # Filter based on visit_confidence, drop all places with less than 50 percent confidence
  filter(visit_confidence >= 50) %>%  
  # Select only the first 6 columns for the visualization only
  select(1:6) %>%                    
  mutate(
    visit_order = seq_len(nrow(.)),
    # Add jitter to avoid overlap
    latitude = jitter(latitude, factor = 0.1),
    longitude = jitter(longitude, factor = 0.1)
  )

# Read GLH data for FD02
data_FD02 <- read.csv("/FD02/place_visit_data/FD02_place_visit.csv")
data_FD02 <- data_FD02 %>%
  # Filter based on visit_confidence, drop all places with less than 50 percent confidence
  filter(visit_confidence >= 50) %>%
  # Select only the first 6 columns for the visualization only
  select(1:6) %>%
  mutate(
    visit_order = seq_len(nrow(.)),
    # Add jitter to avoid overlap
    latitude = jitter(latitude, factor = 0.1),
    longitude = jitter(longitude, factor = 0.1)
  )
```
## Please runthe UI-Server Part for Slider-bar and Clusterer Markers seperately
## Only one app shows at each time

## Slider-bar Visualization
## Define the UI for the APP
```{r}
# Define UI for the Shiny app
ui <- fluidPage(
  titlePanel("Google Location History Viewer"),
  sidebarLayout(
    sidebarPanel(
      sliderInput("visit_count_FD01", "Show locations up to (FD01):", 
                  min = 2, max = nrow(data_FD01), value = 2, step = 1, animate = TRUE),
      sliderInput("visit_count_FD02", "Show locations up to (FD02):", 
                  min = 2, max = nrow(data_FD02), value = 2, step = 1, animate = TRUE)
    ),
    mainPanel(
      leafletOutput("map")
    )
  )
)
```
## Define the server for the APP
```{r}
# Define the server for the app
server <- function(input, output, session) {
  # Render the initial map
  output$map <- renderLeaflet({
    leaflet() %>%
      addTiles() %>%
      addLegend(
        position = "bottomright",
        colors = c("blue", "green", "red"),
        labels = c("FD01 Places", "FD02 Places", "Movement Path"),
        title = "Google Location History"
      )
  })
  
  # Observe changes for FD01
  observe({
    # Filter the data based on the slider value for FD01
    filtered_data_FD01 <- data_FD01[1:input$visit_count_FD01, ] %>%
      filter(!is.na(latitude), !is.na(longitude), !is.na(place_name))
    
    # Prepare arrow data for FD01 if there are enough rows
    if (nrow(filtered_data_FD01) > 1) {
      arrow_data_FD01 <- data.frame(
        from_lat = head(filtered_data_FD01$latitude, -1),
        from_lon = head(filtered_data_FD01$longitude, -1),
        to_lat = tail(filtered_data_FD01$latitude, -1),
        to_lon = tail(filtered_data_FD01$longitude, -1)
      )
    } else {
      arrow_data_FD01 <- NULL
    }
    
    # Update the map for FD01
    leafletProxy("map", data = filtered_data_FD01) %>%
      clearMarkers() %>%
      clearShapes() %>%
      addCircleMarkers(
        ~longitude, ~latitude,
        color = "blue", radius = 4,
        label = ~paste(place_name, "<br>Order:", visit_order),
        labelOptions = labelOptions(noHide = FALSE)
      )
    
    # Add directional arrows for FD01 if valid
    if (!is.null(arrow_data_FD01)) {
      leafletProxy("map") %>%
        addFlows(
          arrow_data_FD01$from_lon, arrow_data_FD01$from_lat,
          arrow_data_FD01$to_lon, arrow_data_FD01$to_lat,
          color = "red", opacity = 0.8, maxFlow = 10
        )
    }
  })
  
  # Observe changes for FD02
  observe({
    # Filter the data based on the slider value for FD02
    filtered_data_FD02 <- data_FD02[1:input$visit_count_FD02, ] %>%
      filter(!is.na(latitude), !is.na(longitude), !is.na(place_name))
    
    # Prepare arrow data for FD02 if there are enough rows
    if (nrow(filtered_data_FD02) > 1) {
      arrow_data_FD02 <- data.frame(
        from_lat = head(filtered_data_FD02$latitude, -1),
        from_lon = head(filtered_data_FD02$longitude, -1),
        to_lat = tail(filtered_data_FD02$latitude, -1),
        to_lon = tail(filtered_data_FD02$longitude, -1)
      )
    } else {
      arrow_data_FD02 <- NULL
    }
    
    # Update the map for FD02
    leafletProxy("map", data = filtered_data_FD02) %>%
      clearMarkers() %>%
      clearShapes() %>%
      addCircleMarkers(
        ~longitude, ~latitude,
        color = "green", radius = 4,
        label = ~paste(place_name, "<br>Order:", visit_order),
        labelOptions = labelOptions(noHide = FALSE)
      )
    
    # Add directional arrows for FD02 if valid
    if (!is.null(arrow_data_FD02)) {
      leafletProxy("map") %>%
        addFlows(
          arrow_data_FD02$from_lon, arrow_data_FD02$from_lat,
          arrow_data_FD02$to_lon, arrow_data_FD02$to_lat,
          color = "red", opacity = 0.8, maxFlow = 10
        )
    }
  })
}

# Run the app
shinyApp(ui = ui, server = server)
```

## Clustered Marker Visualization with Top 5 most visited place displayed, including FD01, FD02, and data for FD02 for March 2020 to December 2020 during the Covid-19 lockdown
## Define the UI for the APP
```{r}
ui <- fluidPage(
  titlePanel("Google Location History Visualization"),
  
  sidebarLayout(
    sidebarPanel(
      h3("Clustered Markers Visualization"),
      p("This map shows clustered markers for two datasets (FD01 and FD02) with additional data for FD01 (March 2020 - December 2020)."),
      
      h4("Top 5 Most Visited Places"),
      
      h5("FD01:"),
      tableOutput("top_places_FD01"),
      
      h5("FD02:"),
      tableOutput("top_places_FD02"),
      
      h5("FD01 (March 2020 - December 2020):"),
      tableOutput("top_places_FD01_MarDec2020")
    ),
    
    mainPanel(
      leafletOutput("map", height = 600)  # Map output
    )
  )
)
```
## Define the server for the APP
```{r}
server <- function(input, output, session) {
  # Filter FD01 data for March 2020 to December 2020
  data_FD01_MarDec2020 <- data_FD01 %>%
    filter(
      as.Date(start_time) >= as.Date("2020-03-01") & 
      as.Date(start_time) <= as.Date("2020-12-31")
    )
  
  # Top 5 most visited places for FD01
  output$top_places_FD01 <- renderTable({
    data_FD01 %>%
      group_by(place_name) %>%
      summarise(visits = n()) %>%
      arrange(desc(visits)) %>%
      slice_head(n = 5)  # Top 5 places
  }, rownames = TRUE)
  
  # Top 5 most visited places for FD02
  output$top_places_FD02 <- renderTable({
    data_FD02 %>%
      group_by(place_name) %>%
      summarise(visits = n()) %>%
      arrange(desc(visits)) %>%
      slice_head(n = 5)  # Top 5 places
  }, rownames = TRUE)
  
  # Top 5 most visited places for FD01 (March 2020 - December 2020)
  output$top_places_FD01_MarDec2020 <- renderTable({
    data_FD01_MarDec2020 %>%
      group_by(place_name) %>%
      summarise(visits = n()) %>%
      arrange(desc(visits)) %>%
      slice_head(n = 5)  # Top 5 places
  }, rownames = TRUE)
  
  # Render the map with clustered markers
  output$map <- renderLeaflet({
    leaflet() %>%
      addTiles() %>%
      
      # FD01 Markers
      addMarkers(
        data = data_FD01,
        lng = ~longitude, lat = ~latitude,
        popup = ~paste("<b>Place Name:</b>", place_name, "<br><b>Visit Order:</b>", visit_order),
        clusterOptions = markerClusterOptions(),
        group = "FD01"
      ) %>%
      
      # FD02 Markers
      addMarkers(
        data = data_FD02,
        lng = ~longitude, lat = ~latitude,
        popup = ~paste("<b>Place Name:</b>", place_name, "<br><b>Visit Order:</b>", visit_order),
        clusterOptions = markerClusterOptions(),
        group = "FD02"
      ) %>%
      
      # FD01 Markers (March 2020 - December 2020)
      addMarkers(
        data = data_FD01_MarDec2020,
        lng = ~longitude, lat = ~latitude,
        popup = ~paste("<b>Place Name:</b>", place_name, "<br><b>Visit Order:</b>", visit_order),
        clusterOptions = markerClusterOptions(),
        group = "FD01 (Mar-Dec 2020)"
      ) %>%
      
      # Add layer control to switch between FD01, FD02, and FD02 (March-Dec 2020)
      addLayersControl(
        overlayGroups = c("FD01", "FD02", "FD01 (Mar-Dec 2020)"),
        options = layersControlOptions(collapsed = FALSE)
      ) %>%
      
      # Add legends
      addLegend(
        position = "bottomright",
        colors = c("blue", "green", "orange"),
        labels = c("FD01 Points", "FD02 Points", "FD01 (Mar-Dec 2020)"),
        title = "Legend"
      )
  })
}

# Run the app
shinyApp(ui = ui, server = server)
```